The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-03-13 analysis/paper/paper.qmd
Update stopword removal in paper

emu_theses$text_clean <- emu_theses$text |>
  clean_basic() |>
  str_remove_all(find_meta_stopwords(emu_theses)) |> 
  str_remove_all(subject_stopwords()) |> 
  str_remove_all(document_stopwords())
```

```{r}
#| label: preview
#| include: false

# Preview theses
emu_theses %>% 
  arrange(graduation_year) %>% 
  pull(text_clean) %>% 
  str_sub(1, 500)

# Preview theses
hist(str_length(emu_theses$text_clean))

Encoding(emu_theses$text_clean)
```

@@

urbanism_stopwords <- urbanism_stopwords() 
thesis_stopwords <- thesis_stopwords()

emu_theses_words <- emu_theses |> 
  select(title, text_clean) |> 
  unnest_tokens(output = word, input = text_clean) |>   # remove punctuation, convert to lowercase, seperate all words
  anti_join(stop_words, by = "word") |> 
  anti_join(urbanism_stopwords, by = "word") |> 
  anti_join(thesis_stopwords, by = "word")
```

>>>>

emu_theses$text_clean <- emu_theses$text |>
  clean_basic() 
```

@@

emu_theses$text_clean <- emu_theses$text_clean |>
  str_remove_all(find_meta_stopwords(emu_theses)) |> 
  str_remove_all(subject_stopwords()) |> 
  str_remove_all(document_stopwords())

emu_theses_words <- emu_theses |> 
  select(title, text_clean) |> 
  unnest_tokens(output = word, input = text_clean) |>   # remove punctuation, convert to lowercase, separate all words
  anti_join(tidytext::stop_words, by = "word")
```
